Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-20 paper-1/manuscript.tex
Editing

This pattern was reflected also in the aggregate across networks and stimuli. Firstly, the contrast (dev - msc) in the target response (Figure \ref{fig7}d, left) was positive in both models, but the full model contrast was greater than the ablated model contrast (t = 2.99, p = 0.00168; one-sided t-test, n = 120). Referring to the previous section, we identify the cause for this in an enhanced contrast in $V_{TA}$, as shown in Figure \ref{fig7}e; the contrast (dev - msc) in the full model was more negative than that in the ablated model (t = -3.49, p = 0.000342). Lastly, returning to Figure \ref{fig7}d (right), we see that the driver of $V_{TA}$, namely the non-target response size, also showed an enhanced contrast (dev - msc) in the full model relative to the ablation (t = -3.19, p = 0.000921). To sum up, the reason for the larger target dev response, relative to msc, was the smaller non-target dev response, relative to msc; furthermore, since the relationships established in the previous section remained largely unchanged, this effect appeared to be mediated primarily through TA.

>>>>

This pattern was reflected also in the aggregate across networks and stimuli. Firstly, the contrast (dev - msc) in the target response (Figure \ref{fig7}d, left) was positive in both models, but the full model contrast was greater than the ablated model contrast (t = 2.99, p = 0.00168; one-sided t-test, n = 120). Referring to the previous section, we identify the cause for this in an enhanced contrast in $V_{TA}$, as shown in Figure \ref{fig7}e; the contrast (dev - msc) in the full model was more negative than that in the ablated model (t = -3.49, p = 0.000342). Lastly, returning to Figure \ref{fig7}d (right), we see that the driver of $V_{TA}$, namely the non-target response size, also showed an enhanced contrast (dev - msc) in the full model relative to the ablation (t = -3.19, p = 0.000921). To sum up, the reason for the larger target dev response relative to msc, was the smaller non-target dev response relative to msc; furthermore, since the relationships established in the previous section remained largely unchanged, this effect appeared to be mediated primarily through TA.
